Geoelectric Field and Electrical Exploration Assignment: Time Sequences Signal Processing in Magnetotelluric Method

### 2025-01-01 Article/main.tex
committed by yang: finish the article.

\received{December 24, 2024}
\revised{December 24, 2024}
\accepted{December 25, 2024}
\published{December 26, 2024}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\columnwidth]{figures/r40-13.eps}
    \caption{The frequency-apparent resistivity curve  using the Dunhuang 1995 40-13 data.}
    \label{fig:r40-13}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\columnwidth]{figures/ph40-13.eps}
    \caption{The frequency-phase curve using the Dunhuang 1995 40-13 data.}
    \label{fig:ph40-13}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\columnwidth]{figures/cp40-13.eps}
    \caption{The coherence curve using the Dunhuang 1995 40-13 data.}
    \label{fig:cp40-13}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\columnwidth]{figures/tp40-13.eps}
    \caption{The amplitude and phase of the tipper using the Dunhuang 1995 40-13 data.}
    \label{fig:tp40-13}
\end{figure}

@@

\begin{figure*}[pb]
    \centering
    \includegraphics[width=0.95\textwidth]{figures/Line40.eps}
    \caption{The frequency-apparent resistivity curve of line 40.}
    \label{fig:Line40}
\end{figure*}

@@

@@

@@

@@

    % \begin{figure}[H]
    %     \centering
    %     \includegraphics[width=0.71\columnwidth]{Example.pdf}
    %     \caption{Example figure obtained from PGFPlots \cite{PFGPlots}.}
    %     \label{fig:figure}
    % \end{figure}

>>>>

\received{December 24, 2024}
\revised{December 26, 2024}
\accepted{January 1, 2024}
\published{January 1, 2024}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.95\columnwidth]{figures/r40-13.eps}
    \caption{The frequency-apparent resistivity curve  using the Dunhuang 1995 40-13 data.}
    \label{fig:r40-13}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.95\columnwidth]{figures/ph40-13.eps}
    \caption{The frequency-phase curve using the Dunhuang 1995 40-13 data.}
    \label{fig:ph40-13}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.95\columnwidth]{figures/cp40-13.eps}
    \caption{The coherence curve using the Dunhuang 1995 40-13 data.}
    \label{fig:cp40-13}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.95\columnwidth]{figures/tp40-13.eps}
    \caption{The amplitude and phase of the tipper using the Dunhuang 1995 40-13 data.}
    \label{fig:tp40-13}
\end{figure}

@@

\begin{figure*}[htpb]
    \centering
    \includegraphics[width=0.95\textwidth]{figures/Line40.eps}
    \caption{The frequency-apparent resistivity curve of line 40.}
    \label{fig:Line40}
\end{figure*}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.95\columnwidth]{figures/et.eps}
    \caption{Electric field strength time series of 0 to 1 second, sampling frequency 4096Hz.}
    \label{fig:et}
\end{figure}

As a supplement to our assignment, we also used additional data \texttt{YJBey.dat} and \texttt{YJBhx.dat}. This set of data gives the electric field strength and magnetic field strength of the time series. The sampling frequency of each channel is 4096Hz and the sampling time is 2 seconds. In order to use linear least squares estimation calculation, we take 0.5s as the time interval to obtain 4 sets of electric field strength and magnetic field strength data. By fast Fourier transform of the time series, four power spectra are obtained, as shown in the Figure.\ref{fig:ef}.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.95\columnwidth]{figures/ef.eps}
    \caption{Amplitude spectrum of electric field intensity}
    \label{fig:ef}
\end{figure}

The calculated apparent resistivity curve and phase curve are shown in the Figure.\ref{fig:yjb-ra} and Figure.\ref{fig:yjb-ph}.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.95\columnwidth]{figures/YJBra.eps}
    \caption{The apparent resistivity curve.}
    \label{fig:yjb-ra}
\end{figure}

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.95\columnwidth]{figures/YJBph.eps}
    \caption{The phase curve.}
    \label{fig:yjb-ph}
\end{figure}

Again, a one-dimensional bostick inversion is performed on this result to obtain the underground resistivity, as shown in the Figure.\ref{fig:yjb-r}.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.95\columnwidth]{figures/YJBbostick.eps}
    \caption{One-dimensional bostick inversion result curve.}
    \label{fig:yjb-r}
\end{figure}

@@

In this semester's assignment, we derived the linear least squares estimation formula for impedance in the magnetotelluric method. Using this formula, we calculated the apparent resistivity curve and phase curve for the 1995 Dunhuang Line 40 data, as well as the coherence and tipper vector. Based on the coherence analysis, it was found that the data quality was suboptimal, leading to significant deviations in the results obtained from one-dimensional Bostick inversion. Additionally, we processed magnetotelluric sounding data from supplementary operations, performing one-dimensional Bostick inversion which yielded satisfactory results.

Through this semester's project, team members gained a deeper understanding of the fundamental theory and practical applications of the magnetotelluric method. We also acquired skills in impedance estimation and necessary programming techniques. Furthermore, our comprehension of forward and inverse modeling in electrical exploration has been significantly enhanced.

@@

Professor Jiabin Yan gave guidance for this assignment. Researcher Xiaozhong Tong provided rich and valuable suggestions for group. Professors Haifei Liu and Rujun Chen also provided advice to the group.

@@

    % \begin{figure}[htbp]
    %     \centering
    %     \includegraphics[width=0.71\columnwidth]{Example.pdf}
    %     \caption{Example figure obtained from PGFPlots \cite{PFGPlots}.}
    %     \label{fig:figure}
    % \end{figure}
